Paper \#ZW10157

### 2019-01-15 paper/submission/ZW10157-response-1.tex
more small edits to review response 1

First, optimization systems based on PISA have been in use in
accelerator design since 2005, and NSGA-II’s use dates from that time
too. References to early PISA-based systems and NSGAII applications
are missing from the authors’ reference list, and the authors must
correct this. Three groups of references are provided to assist in
addressing these omissions: 1) early PISAbased systems; 2) a small
sample of NSGA-II applications and implementations (there are MANY
more as the NSGA-II algorithm is easy to understand and fairly
straight forward to implement); and 3) a survey of accelerator physics
and genetic and evolutionary application usage as of 2013.

@@

@@

@@

{\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
Especially, the following:

}

Second, due to the thoroughness and success of Bazarov and Sinclair’s
optimization (PRSTAB 2005 provided above), genetic and evolutionary
algorithm-based optimizations are standard practice in accelerator
design, and researchers are now looking at ways to use machine
learning and AI techniques in accelerator design and optimization.
Manual parameter scans, as mentioned in Section I lines 17-19, are
useful, but they are by no means the sole optimization technique in
use today. The statement made in lines 17-19 was true prior to 2005
but not now. The authors should consider providing a different and
more compelling motivator to encourage users to consider the system
they have developed.

>>>>

References to early PISA-based systems and NSGAII applications
are missing from the authors’ reference list, and the authors must
correct this. Three groups of references are provided to assist in
addressing these omissions: 1) early PISAbased systems; 2) a small
sample of NSGA-II applications and implementations (there are MANY
more as the NSGA-II algorithm is easy to understand and fairly
straight forward to implement); and 3) a survey of accelerator physics
and genetic and evolutionary application usage as of 2013.

{\bf Our response:} {\color{blue} We agree that some references of import were missing and should have been included.
	Especially the following:

	We thank the reviewer for the list of references. 
	References described or referenced by A. Hofler in the above were excluded from 
	the bibliography. 
}

@@

{\color{blue}{Included in updated bib:}}

@@

{\color{blue}{Exluded from bib, because  they are in A. Hofler 13':}}

@@

Manual parameter scans, as mentioned in Section I lines 17-19, are
useful, but they are by no means the sole optimization technique in
use today. The statement made in lines 17-19 was true prior to 2005
but not now. The authors should consider providing a different and
more compelling motivator to encourage users to consider the system
they have developed.

### 2019-01-15 paper/submission/theor-experiment.tex
more small edits to review response 1

\iffalse
%\vspace{0.2cm}
\begin{samepage}
	\begin{Verbatim}[fontsize=\scriptsize]
	OPTION, ECHO=FALSE;
	OPTION, INFO=TRUE;

	TITLE, STRING="ANL Optimization";

	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=200.0, UPPERBOUND=500.0;
	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=170.0, UPPERBOUND=260.0;
	dv2: DVAR, VARIABLE="GPHASE", LOWERBOUND=-30.0, UPPERBOUND=0.0;
	dv3: DVAR, VARIABLE="FWHM",   LOWERBOUND=1.5,   UPPERBOUND=10.0;

	// Quad values
	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;

	rmss1:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',16.5))";
	emitx1: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',16.5))";

	rmss2:  OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',18.5))";
	emitx2: OBJECTIVE,EXPR="fabs(statVariableAt('emit_x',18.5))";

	c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<1.0e-1";
	c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<1.0e-1";

	OPTIMIZE, INPUT="tmpl/optLinac_40nC.tmpl",
	OUTPUT="optLinac_40nC",
	OUTDIR="results",
	OBJECTIVES = {rmss1, emitx1, rmss2, emitx2},
	DVARS = {dv0, dv1, dv2, dv3, dv4, dv5, dv6, dv7},
	CONSTRAINTS = {c1, c2},
	INITIALPOPULATION=80,
	MAXGENERATIONS=100,
	NUM_MASTERS=1,
	NUM_COWORKERS=8,
	SIMTMPDIR="tmp",
	TEMPLATEDIR="tmpl",
	\end{Verbatim}
\end{samepage}
\fi
%\vspace{0.2cm}

@@

Equations (\ref{eq:awa:firstconstr}) to
(\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
laser radius, gun phase, and linac cavity phases (in that order). 
These are parameters in the simulation 
that must be defined, but do not vary during the optimization.
%\vspace{-1em}
The AWA 
design variables, objectives, and constraints in the OPAL input file as shown in
the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}). 
%\vspace{0.2cm}
\iffalse
\begin{samepage}
	\begin{Verbatim}[fontsize=\scriptsize]

	// Gun variables 
	dv0: DVAR, VARIABLE="IBF",    LOWERBOUND=300.0, UPPERBOUND=500.0;
	dv1: DVAR, VARIABLE="IM",     LOWERBOUND=180.0, UPPERBOUND=280.0;

	// Quad variables 
	dv4: DVAR, VARIABLE="KQ1", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv5: DVAR, VARIABLE="KQ2", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv6: DVAR, VARIABLE="KQ3", LOWERBOUND=-8.0, UPPERBOUND=8.0;
	dv7: DVAR, VARIABLE="KQ4", LOWERBOUND=-8.0, UPPERBOUND=8.0;

	//Objectives
	de3: OBJECTIVE,EXPR="fabs(statVariableAt('dE',19.4))";
	rmss3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_s',19.4))";
	rmsx3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_x',19.4))";
	rmsy3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_y',19.4))";
	rmspx3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_px',19.4))";
	rmspy3: OBJECTIVE,EXPR="fabs(statVariableAt('rms_py',19.4))";

	//Constraints
	c1: CONSTRAINT, EXPR="fabs(statVariableAt('rms_x',16.5))<0.1";
	c2: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5))<0.1";
	c3: CONSTRAINT, EXPR="fabs(statVariableAt('rms_y',16.5)
	-statVariableAt('rms_x',16.5))<0.005";

	OPTIMIZE, INPUT="tmpl/optLinac-40nC.tmpl",
	OUTPUT="optLinac-40nC",
	OUTDIR="results",
	OBJECTIVES = {rmss3, rmsx3, rmsy3, rmspx3, rmspy3, de3},
	DVARS = {dv0, dv1, dv4, dv5, dv6, dv7},
	CONSTRAINTS = {c1, c2, c3},
	INITIALPOPULATION=656,
	MAXGENERATIONS=200,
	NUM_MASTERS=1,
	NUM_COWORKERS=8,
	SIMTMPDIR="tmp",
	TEMPLATEDIR="tmpl",
	FIELDMAPDIR="fieldmaps",
	NUM_IND_GEN=328,
	GENE_MUTATION_PROBABILITY=0.01,
	MUTATION_PROBABILITY=0.01,
	RECOMBINATION_PROBABILITY=0.09;
	QUIT;
	\end{Verbatim}
\end{samepage}
\fi

>>>>

@@

Equations (\ref{eq:awa:firstconstr}) to
(\ref{eq:awa:lastdvar}) define the charge, gun voltage, linac voltages, 
laser radius, gun phase, and linac cavity phases (in that order). 
These are parameters in the simulation 
that must be defined, but do not vary during the optimization.
%\vspace{-1em}
The AWA 
design variables, objectives, and constraints in the OPAL input file as shown in
the following code: %equations (\ref{eq:awa:p1}) to (\ref{eq:awa:lastdvar}). 
%\vspace{0.2cm}
